Understanding the technological transition based on cultural transmission biases during the Late Pleistocene in Korea

### 2021-02-01 analysis/paper/paper.Rmd
organize codes to each r script

Computing size attributes  of the points by calculating distance between landmarks
```{r}

@@

The coefficient of variation (CV) is the ratio of the standard deviation devided by mean. It shows the extent of variability from the mean.

@@

library(tidyr)
cv_plot_stage %>% 
pivot_longer(cols = -SPstage.Stage, names_to = "group") %>%
ggplot(aes(x = group, y = value, fill = as.factor(SPstage.Stage))) + 
geom_bar(stat="identity", position=position_dodge()) + labs(x="Attributes", fill= "Phase")

@@

library(tidyr)
p<- cv_plot_site_label %>% 
pivot_longer(cols = -c(sitename,label), names_to = "group") %>% 
ggplot(aes(label, value, fill = as.factor(group))) + 
geom_bar(stat="identity", position=position_dodge())

@@

We see some differences in artefact shape and size. Now we need to examins the PCA output numbers to describe in more details.

>>>>

```{r}
#Computing size attributes  of the points by calculating distance between landmarks

@@

The coefficient of variation (CV) is the ratio of the standard deviation divided by mean. It shows the extent of variability from the mean.

@@

cv_plot_stage %>% 
pivot_longer(cols = -SPstage.Stage, names_to = "group") %>%
ggplot(aes(x = group, y = value, fill = as.factor(SPstage.Stage))) + 
geom_bar(stat="identity", position=position_dodge()) + labs(x="Attributes", fill= "Phase")

@@

p<- cv_plot_site_label %>% 
pivot_longer(cols = -c(sitename,label), names_to = "group") %>% 
ggplot(aes(label, value, fill = as.factor(group))) + 
geom_bar(stat="identity", position=position_dodge())

@@

We see some differences in artefact shape and size. Now we need to examines the PCA output numbers to describe in more details.
